Four reasons your build is slow

### 2019-01-17 paper.tex
rewrite conclusion

\begin{abstract}
Spending time waiting for code to compile is cliche enough to be
featured in XKCD, yet it continues to plague software
developers. Fortunately, software builds are an embarassingly parallel
problem, and so we can finally make use of all those extra cores---a
happy coincidence of software complexity and hardware trends.

Unfortunately, the story is not quite this rosy, as almost anyone who
waits for software to build knows. Real build systems fail to be the
embarassingly parallel poster child we hope for, and instead are slow
in a wide variety of ways.

@@

If you develop software, or even if you compile it, you probably run
into software that's slow to build. This problem is such a cliche that
it appears in comics, but it's also such a problem that companies
routinely outfit developers with the beefiest machines possible---all
to compile software projects faster. Fortunately, for most systems and
languages, compiling software is a classic example of embarassing
parallelism. As a result, developers who spend much of their time
compiling large software projects use highly parallel systems to do so
[cite Regehr tweet].

@@

However, this seeming solution rarely works out as well in practice as
it does in theory. In addition to the substantial expense of
highly-parallel systems, real software rarely makes use of the full
capacity of the machine it is built on, despite the potential for high
degrees of parallelism.

@@

\section{Future work}

One of the limitations of this work is that currently to collect the necessary data to reconstruct
the build graph, the project must be built using a single thread.  This is a burden for projects
that are very long running, such as LLVM.  Additionally, building with strace causes an additional
slowdown and inflates the running time of each shell command, which makes the raw numbers
reported by a build graph created with strace on, inaccurate.  In the future for performance sake
it would be good to collect the necessary information while allowing make to run in parallel with
any number of processes.  It would also be good to know how much strace perturbs the recorded
time of any given shell command so both the tool with and without strace don't need to be run.

In addition to this, we hope to analyse more project builds and introduce parallelism at other
level of project builds, such as at the level of the compiler.

>>>>

\begin{abstract}
Spending time waiting for code to compile is cliche enough to be
featured in XKCD, yet it continues to plague software
developers. Fortunately, software builds are an embarassingly parallel
problem, and so we can finally make use of all those extra cores---a
happy coincidence of software complexity and hardware trends.
%
Unfortunately, the story is not quite this rosy, as almost anyone who
waits for software to build knows. Real build systems fail to be the
embarassingly parallel poster child we hope for, and instead are slow
in a wide variety of ways.

@@

If you develop software, or even if you compile it, you probably run
into software that's slow to build. This problem is such a cliche that
it appears in comics, but it's also such a problem that companies
routinely outfit developers with the beefiest machines possible---all
to compile software projects faster. Fortunately, for most systems and
languages, compiling software is a classic example of embarassing
parallelism. As a result, developers who spend much of their time
compiling large software projects use highly parallel systems to do so
\cite{regehr-tweet}.

@@

However, this seeming solution rarely works out as well in practice as
it does in theory. In addition to the substantial expense of
highly-parallel systems, real software rarely makes use of the full
capacity of the machine despite the potential for high
degrees of parallelism.

@@

\section{Conclusion}

We present an automated analysis tool for build systems based on
\verb|make|, which can automatically determine the available
parallelism in a build process and provide useful information to
improve it. Our tool makes use of \verb|strace| instrumentation to
determine the ground truth about the build process, and can answer
counterfactual questions about how much a build could improve.
%
We show four case studies on three real software projects
demonstrating the power of our analysis and point to sources of
slowdown and lack of parallelism, and use our tool to make
improvements that substantially increase parallelism.

The case studies we've shown already demonstrate the value of our
tool, but extensions could make it more useful to developers and build
system authors---for example, by automatically generating revised
\verb|Makefile|s or by using \verb|strace| to instrument arbitrary
build systems, not just \verb|make|. Finally, we hope to integrate
this with an analysis of parallelism in commands executed by the build
system, such as the \verb|gold| linker.
